---
title: Your turns
format: html
---

Loading all packages we will be using.

```{r}
# pak::pak(c("recipes", "embed", "extrasteps"))
library(recipes)
library(embed)
library(extrasteps)

# pak::pak("emilhvitfeldt/animalshelter")
library(animalshelter)
```


Explore the `animalshelter::longbeach` data set, using whatever tools you prefer.

```{r}
longbeach
```

## Numerics

Apply some of the methods we have learned so far to the data set.

Distribution: 
- `step_log()`
- `step_sqrt()`
- `step_BoxCox()`
- `step_YeoJohnson()`

Scaling:
- `step_normalize()`
- `step_scale()`
- `step_center()`

Splines:
- `step_spline_b()`
- `step_spline_convex()`
- `step_spline_monotone()`
- `step_spline_natural()`
- `step_spline_nonnegative()`

```{r}
rec <- recipe(~., data = longbeach)
# add steps here
```

```{r}
rec |>
  prep() |>
  bake(new_data = NULL)
```

## Categoricals

Apply some of the methods we have learned so far to the data set

Label encoding: 
- `step_integer()`

Dummy encoding: 
- `step_dummy()`

frequency encoding: 
- `extrasteps::step_encoding_frequency()`

target encoding: 
- `embed::step_lencode()`
- `embed::step_lencode_glm/mixed/bayes()`

```{r}
rec <- recipe(~., data = longbeach)
# add steps here
```

```{r}
rec |>
  prep() |>
  bake(new_data = NULL)
```

## Date Time

Apply some of the methods we have learned so far to the data set

Extraction: 
- `step_date()`

Special days: 
- `step_holiday()`

nearby: 
- `extrasteps::step_date_before()`
- `extrasteps::step_date_after()`
- `extrasteps::step_date_nearest()`

```{r}
rec <- recipe(~., data = longbeach)
# add steps here
```

```{r}
rec |>
  prep() |>
  bake(new_data = NULL)
```
